Chain separation distribution in protein contact networks

### 2022-03-21 paper/main.tex
testing if this works.

Here we have introduced and analyzed the amino acid distance $s$ and its probability distribution $P(s)$ in measured and simulated protein structures. For the equivalent model in two dimensions we have used a mean-field approach to derive an analytic approximation for the amino acid distance distribution, which appears to agree with the simulated and measured distributions.
We have thus demonstrated in analytical calculations as well as direct simulations how a random linking model with geometric constraints, such as the ones introduced in \cite{molkenthin2016scaling, molkenthin2020self}, generates a amino acid distance distribution that resembles a power-law, similar to the one found in folded proteins. This feature of protein network structures has previously been used in a heuristic manner to model and generate protein-like structures in \cite{bartoli2008effecta}.

>>>>

Here we have introduced and analyzed the amino acid distance $s$ and its probability distribution $P(s)$ in measured and simulated protein structures. For the equivalent model in two dimensions we have used a mean-field approach to derive an analytic approximation for the amino acid distance distribution, which appears to agree with the simulated and measured distributions.
We have thus demonstrated in analytical calculations as well as direct simulations how a random linking model with geometric constraints, such as the ones introduced in~\cite{molkenthin2016scaling, molkenthin2020self}, generates a amino acid distance distribution that resembles a power-law, similar to the one found in folded proteins. This feature of protein network structures has previously been used in a heuristic manner to model and generate protein-like structures in \cite{bartoli2008effecta}.
